Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-04 2016-Weak-FH-Bisim/WeakBisim.tex
finished the equations page 49
Bug lemma 6
current proof state
premiere passe notation lemma 7
working on proof of lemma 6

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $n$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p= \beta_p\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i) 
\\
\text{and~}
\Post=\Post\,' \uplus \bigotimes_{p=n}^0
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

@@

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT}, denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where:\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
 for all $l\in L$: 
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
and \\%$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
$\set{\gamma}_j=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=0}^{m_2}
\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}\land\Pred'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\land\\ 
~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\\
\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$

Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps. In other words, if there is $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.  we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ by $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$. Note that if $Q$ does an OT staying at the same state, we keep this necessary OT. We proceed in the same way  for states named $u$. To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
$\forall p\! \in\! [0..n_1] Q\models{\openrule
			{
				(\beta'_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
				{{\Post''_{1p}}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$
$ Q\models{\openrule
			{
				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0..n_2] Q\models{\openrule
			{
				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
				{{\Post''_{3p}}}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$.\\
By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
				{{\Post''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, then there is an action $\beta$ such that $\beta=\beta_{1p j_0}$ s.t. $j_0\in J_{1p}$, or $\beta=\beta_{2 j_0}$ with $j_0\in J_{2}$, or $\beta=\beta_{3p j_0}$ s.t. $j_0\in J_{3p}$, where $\beta=\alpha_k$, additionally the different $\beta$ are ordered by following the OTs, somehow performing the same re-indexing as  the removal of steps where $Q$ does not move above. Overall we have\footnote{under the assumption written above, i.e. that $Q$ moves in the middle OT, i.e. $j_0\in J_{2}$}:
\[
[\beta_{1 p j_0}|j_0\in J_{1p}]\dotcup [\beta_{2 j_0}] \dotcup [\beta_{3 p j_0}|j_0\in J_{3p}] = [\alpha_0..\alpha_{n_1+n_2+2}]
\]

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences; for $k\in [1..n]$ the position of the $k^{\text{th}}$ visible action is is $n_k$, $k\in [1..n-1]$ for  $n'_k$ is any index between $n_k$ and $n_{k+1}$,  $n'_0=0$ and $n'_n=n_1+n_2+3$. We obtain $n$ subsequences  made of the following OTs, for all $k\in [1..n]$ :\\
$\forall p\! \in\! [n'_{k-1}..(n_k\!-\!1)] Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
				{{\Post''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred''_{n_k}}},  
				{{\Post''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n_k\!+\!1)..(n_k'\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
				{{\Post''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{(v_{l}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\alpha_k'=\alpha_k\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'{k-1}}\!\!\Post''_{p}}}$\\
$\forall l \in L_Q. v_l=v_{(n'_{k-1})l} \wedge v_l'=v_{(n'_k-1)l}$, \\
$\forall j \in  (J\cap\Holes(Q)),\,$
$\displaystyle{\gamma_{kj} }=\displaystyle{\mybigdotcup_{i=n_k-1}^{0} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{1j}}}\dotcup \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=0}^{n_k-1}\!\!\!\Post''_{1j}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=n_k+1}^{n_k'-1}
\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\!\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}} }\\
\Pred_k=\bigwedge_{i=0}^{n_k-1}\!\!\Pred''_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred''_2 \subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}}\land\\ 
~\qquad\quad\bigwedge_{i=n_k+1}^{n_k'-1}\!\!\!\Pred''_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\!\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}}\\
\Post_k= \bigotimes_{j=n_k'-1}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\!\!\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}$\\

In this case, the number of weak open transitions
might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
We have: 
$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{\set{\beta_{2i}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}}$. Additionally, we have
$[\alpha'_0.. \alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$. In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{\set{\beta_{2i}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}} = [\alpha'_0.. \alpha'_n]}$. This ensures that $\gamma_{j_0}=[\alpha'_0.. \alpha'_n]$.

@@

Consequently, for  $\gamma_{j_0}=[\beta_0..\beta_n]$ such that $\beta_i=\alpha'_i$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0..n]$.
Therefore, we can conclude that we have for all $k\in [0..n]$:  
Q\models{\openrule
			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
We have by 	hypothesis: 	$s_{0l}=s_l$, $s_{(n+1)l}=s'_l$\\
By considering $n=m_1+m_2+2$,  and $\forall p \in [0..n]$: \\
$\Pred_{p}= \left\{
 \begin{array}{ll}
\Pred_{1p} & \mbox{if }p<m_1\\
\Pred_{2} & \mbox{if } p=m_1\\
\Pred_{1(p-m_1)} & \mbox{if }p\geq m_1\\
\end{array}
\right. 
\quad$
 $\qquad
\Post_{p}= \left\{
 \begin{array}{ll}
\Post_{1p} & \mbox{if }p<m_1\\
\Post_{2} & \mbox{if } p=m_1\\
\Post_{1(p-m_1)} & \mbox{if }p\geq m_1\\
\end{array}
\right. 
$\\
and similarly for $\beta_p$. Thus, we can rewrite $\gamma$ given in the hypothesis as: \\
$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
\vis{\set{\beta_{p}}}\subst{\bigotimes_{p=n}^{0} \Post_{p}}}$\\
Furthermore, still by hypothesis we have:\\
$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\land \\
~\qquad \quad \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\

>>>>

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $n$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p\bigotimes_{i=p-1}^{0}\Post_i) = \beta_p\land (\Pred_p\bigotimes_{i=p-1}^{0}\Post_i) )
\\
\text{and~}
\Post=\Post\,' \uplus \bigotimes_{p=n}^0
		\Post_p  
		\end{mathpar} 
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

@@

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT}, denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				(\gamma_j')^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where:\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
 for all $l\in L$: 
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
and \\%$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=0}^{m_2}
\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}\land\Pred'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\land\\ 
~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\\
\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$

Note that for all $j\in J\setminus \Holes(Q)$, $\gamma_j' = \gamma_j$ because for all $l$ $\Post'_{1l}$ coincide with $\Post_{1l}$ on the variables of $\beta_{1ij}$, and similarly for $\Post'_2$ and $\Post'_{3l}$.
%Concerning $\gamma'_{j_0}$ we have:
%\[\gamma'_{j_0}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\alpha_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
%~~\qquad \mybigdotcup_{i=0}^{m_2}
%\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\]

Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps. In other words, if there is $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.  we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ by $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$. Note that if $Q$ does an OT staying at the same state, we keep this necessary OT. We proceed in the same way  for states named $u$. To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
$\forall p\! \in\! [0..n_1] Q\models{\openrule
			{
				(\beta_{1p})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
				{{\Post''_{1p}}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$
$ Q\models{\openrule
			{
				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0..n_2] Q\models{\openrule
			{
				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
				{{\Post''_{3p}}}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$.\\
By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
				{{\Post''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p$ (following the re-indexing done in the removal of steps where $Q$ does not move) $\Pred_{1p}\implies \alpha_{1p}=\beta_{1 p j_0}=\alpha_k$ and thus $\Pred_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\implies \beta_{1 p j_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}=\alpha_k\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}}$ (because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$). Finally because $\Post''_{1j}$ is only definesd when $Q$ moves:
\[\Pred_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\implies
 \beta_{1 p j_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}=\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post''_{j}}\]
We have similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the following $\alpha_k$ related with $\beta_{3 j_0}$ for some $p$. Note that the substitutions are however more complex. \TODO{detailler les equations?}

Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform) \[\Pred \implies \gamma_{j_0}=
\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{j}}|p\in[0..n_1+n_2+2]]}\]

%, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, then there is an action $\beta$ such that $\beta=\beta_{1p j_0}$ s.t. $j_0\in J_{1p}$, or $\beta=\beta_{2 j_0}$ with $j_0\in J_{2}$, or $\beta=\beta_{3p j_0}$ s.t. $j_0\in J_{3p}$, where $\beta=\alpha_k$, additionally the different $\beta$ are ordered by following the OTs, somehow performing the same re-indexing as  the removal of steps where $Q$ does not move above. Overall we have\footnote{under the assumption written above, i.e. that $Q$ moves in the middle OT, i.e. $j_0\in J_{2}$}:
%\[ \Pred_* \implies
%[\beta_{1 p j_0}|j_0\in J_{1p}]\dotcup [\beta_{2 j_0}] \dotcup [\beta_{3 p j_0}|j_0\in J_{3p}] = [\alpha_0..\alpha_{n_1+n_2+2}]
%\]
%
%And thus \[\gamma_{j_0} = []\]

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences; for $k\in [1..n]$ the position of the $k^{\text{th}}$ visible action is is $n_k$, $k\in [1..n-1]$ for  $n'_k$ is any index between $n_k$ and $n_{k+1}$,  $n'_0=0$ and $n'_n=n_1+n_2+3$. We obtain $n$ subsequences  made of the following OTs, for all $k\in [1..n]$ :\\
$\forall p\! \in\! [n'_{k-1}..(n_k\!-\!1)] Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
				{{\Post''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred''_{n_k}}},  
				{{\Post''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n_k\!+\!1)..(n_k'\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
				{{\Post''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{(v_{l}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{p}}}$\\
$\forall l \in L_Q. v_l=v_{(n'_{k-1})l} \wedge v_l'=v_{(n'_k-1)l}$, \\
$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k-1}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k-1}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{l}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=n_k+1}^{n_k'-1}
\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post''_{l}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{l}} }\\
%
\Pred_k=\bigwedge_{i=n'_{k-1}}^{n_k\!-\!1}\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k-1}}\!\!\Post_{j}}\land\Pred''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{j}}\land\\ 
~\qquad\quad\bigwedge_{i=n_k+1}^{n_k'-1}\!\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k-1}}\!\!\!\Post''_{j}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{j}}
\\
\Post_k= \bigotimes_{j=n_k'-1}^{n'_{k-1}}\!\!\Post''_{j}$\\

%In this case, the number of weak open transitions
%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
Note that \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{p}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k-1}}^{0}\!\!\Post''_{p}}} = 
\alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{p}}}\]
We now have: \TODO{add ref to eq 1 page above?}
\[\Pred \implies \gamma_{j_0}=
\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\]

%$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{{\beta_{2j_0}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}}$. Additionally, we have
%$[\alpha'_0.. \alpha'_n]$ is the list of non-$\tau$ $\alpha_p$.
%% such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$. 
%In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{{\beta_{2j_0}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}} = [\alpha'_0.. \alpha'_n]}$. %This ensures that $\gamma_{j_0}=[\alpha'_0.. \alpha'_n]$.
%
%
%Consequently

@@

\TODO{stopped here not sure about the following}
